Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-15 paper.tex
fix pyjac version
sp

\revise{The new formulation for \texttt{pyJac}, including both constant-volume and constant-pressure assumptions, resulted in highly sparse chemical kinetic Jacobians.
Though the Jacobian approximation discussed in~\cref{S:sparsity} is not a key feature of this work, future efforts to develop more sophisticated Jacobian approximations would be a worthwhile endevour.}

@@

\add{The results for this article were obtained using \texttt{pyJac v2.x.x}~\cite{pyjac2}.
The most recent version of \texttt{pyJac} can be found at its GitHub repository:
\url{https://github.com/SLACKHA/pyJac}.
All figures, and the data and plotting scripts necessary to reproduce them,
are available openly under the CC-BY license~\cite{data}.}

>>>>

\revise{The new formulation for \texttt{pyJac}, including both constant-volume and constant-pressure assumptions, resulted in highly sparse chemical kinetic Jacobians.
Though the Jacobian approximation discussed in~\cref{S:sparsity} is not a key feature of this work, future efforts to develop more sophisticated Jacobian approximations would be a worthwhile endeavor.}

@@

\add{The results for this article were obtained using \texttt{pyJac v2.0.0b0}~\cite{pyjac2}.
The most recent version of \texttt{pyJac} can be found at its GitHub repository:
\url{https://github.com/SLACKHA/pyJac}.
All figures, and the data and plotting scripts necessary to reproduce them,
are available openly under the CC-BY license~\cite{data}.}
